\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}
\setlist[itemize]{noitemsep, topsep=1pt, leftmargin=1.1em}
\setlength{\parskip}{2pt}

\begin{document}

\begin{center}
    {\LARGE\textbf{Emilio Gordillo Esparragoza}}\\[3pt]
    Data Engineer \& Backend Developer\\[4pt]
    \href{mailto:emilio.gordillo.dev@gmail.com}{emilio.gordillo.dev@gmail.com}
    $\cdot$ Mexico
    $\cdot$ \href{https://github.com/Emilio-Gordillo-Esparragoza}{github.com/Emilio-Gordillo-Esparragoza}
    $\cdot$ \href{https://www.linkedin.com/in/emilio-gordillo-esparragoza-948267397/}{LinkedIn}
\end{center}

\section*{Professional Summary}
Aspiring Data Engineer and Backend Developer with hands-on experience in Python, SQL/PostgreSQL, and cloud-native AWS architectures. Currently building production bus-route systems with TypeScript, Supabase, and PostgreSQL while earning a Software Engineering degree. Proven ability to design data preprocessing pipelines, automate DevOps tooling, and implement serverless event-driven patterns (Lambda, SQS, EventBridge, Terraform). Eager to contribute to ETL/ELT pipelines, APIs, and reliable backend services in a data-driven team.

\section*{Technical Skills}
\textbf{Languages:} Python, SQL, TypeScript/JavaScript, PLpgSQL, Java, Rust\\
\textbf{Data \& Analytics:} PostgreSQL, Pandas, NumPy, Apache Spark, scikit-learn, statistical analysis (ANOVA, t-tests)\\
\textbf{Cloud \& Backend:} AWS (Lambda, SQS, EventBridge, serverless), REST APIs, Supabase, FastAPI, Flask\\
\textbf{DevOps \& Tools:} Docker, Terraform, CI/CD (GitHub Actions, Jenkins), Ansible, Nginx, Git

\section*{Experience}

\textbf{Software Developer} \hfill June 2026 -- Present\\
\href{https://www.enrutate.com/}{Enrutate} --- Culiac\'an \& Guasave transit platform\\
\begin{itemize}
    \item Engineer and maintain a production bus route tracking application serving multiple cities using TypeScript/JavaScript, Supabase, and PostgreSQL (PLpgSQL).
    \item Implement real-time data updates and server-side validations to improve route accuracy and user experience for daily riders.
    \item Collaborate on backend data models and queries that support reliable tracking and operational consistency.
\end{itemize}

\section*{Projects}

\textbf{\href{https://github.com/Emilio-Gordillo-Esparragoza/thinking-serverless}{thinking-serverless}} --- AWS Serverless \& Event-Driven Architecture\\
\begin{itemize}
    \item Built deployable reference projects covering EventBridge fan-out, SQS/Lambda async workflows, FIFO queues, and dead-letter queues (DLQ).
    \item Provisioned infrastructure with Terraform and documented scalability, idempotency, and fault-tolerance patterns for distributed cloud systems.
\end{itemize}

\textbf{\href{https://github.com/Emilio-Gordillo-Esparragoza/naim-simple}{naim-simple}} --- ML Missing-Data Pipeline (Python)\\
\begin{itemize}
    \item Developed a scikit-learn-style fit/predict/save/load API that wraps NAIM imputation for tabular datasets.
    \item Abstracted complex preprocessing into reusable components to accelerate model training workflows.
\end{itemize}

\textbf{\href{https://github.com/Emilio-Gordillo-Esparragoza/devtool-pack}{devtool-pack}} --- Cross-Platform DevOps Environment Automation\\
\begin{itemize}
    \item Built a modular Python package that automates installation of Terraform, AWS CLI, Docker, kubectl, and related tooling across Windows, macOS, and Linux.
    \item Reduced multi-tool environment setup from hours to a single command for reproducible developer workstations.
\end{itemize}

\textbf{\href{https://github.com/Emilio-Gordillo-Esparragoza/PonyFlow}{PonyFlow}} --- Multi-Agent Code Generation System\\
\begin{itemize}
    \item Designed a self-correcting multi-agent Python pipeline (planner $\rightarrow$ coder $\rightarrow$ reviewer) using local LLMs with LangChain/Ollama.
    \item Delivered a React + Tauri (Rust) desktop UI to monitor workflows with minimal external dependencies.
\end{itemize}

\section*{Education}
\textbf{Universidad Aut\'onoma de Guadalajara (UAG)} \hfill 2026 -- Present\\
Software Engineering

\section*{Certifications}
IBM Data Engineering Professional Certificate $\cdot$
AWS Academy Cloud Foundations $\cdot$
AWS CloudQuest: Cloud Practitioner $\cdot$
AWS Academy Generative AI Foundations $\cdot$
IBM Applied Software Engineering Fundamentals

\section*{Languages}
English --- Fluent \quad|\quad Spanish --- Native

\end{document}
